\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother


\date{}

\begin{document}

{\ldots{}.28\ldots{}.}

{The other man says, " If you give me 10 rupees, I shall be six times
yourself." Tell me the wealth of each of them.}

{माणिक्याष्टकमिन्द्रनीलदशकं मुक्ताफलानां शतं }

{यत्ते कर्णविभूषणे समधनं क्रीतं त्वदर्थे मया । }

{तद्रत्नत्रयमौल्यसंयुतिमितिस्त्र्यूनं शतार्धं प्रिये }

{मौल्यं ब्रूहि पृथग्यदीह गणिते कल्पाऽसि कल्याणिनि ।। ९४ ।। }

{A man says to his wife, " Do you know that I have purchased 8 rubies,
10 saphires and 100 pearls for your earrings. Each time I paid the same
amount. The price of a set of three jewels i. e. one ruby, one saphire
and one pearl is 47 rupees. Calculate and tell me the price of each
jewel separately."}

{पञ्चांशोऽलिकुलात्कदम्बमगमव्यंशः शिलीन्ध्रं तयोर् - }

{विश्लेषस्त्रिगुणो मृगाक्षि कुटजं दोलायमानोऽपरः । }

{कान्ते केतकमालतीपरिमलप्राप्तैककालीप्रियाद् }

{दूताहूत इतस्ततो भ्रमति खे भृङ्गोऽलिसंख्यां वद ।। ९५ ।। }

{A man says to his wife, " There was a cluster of bees. One fifth went
to kadamb, one third went to mushroom, thrice the difference of these
two numbers went to kutaj. And the remaining one is wandering to and fro
being in doubt as to which of the two ketak or malati has sent
invitation to him through its fragrance. Tell me the total number of
bees."}

{पञ्चकशतदत्तधनात्फलस्य वर्गं विशोध्य परिशिष्टम् । }

{दत्तं दशकशतेन तुल्यः कालः फलं च तयोः ।। ९६ ।। }

{A sum was lent out at 5 per cent per month. Subtracting the square of
the interest for some period from the sum, the remainder was lent out at
10 p. c. p. m. To produce the same interest as before, time required was
the same. Find the\\
}

\end{document}
