\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother


\date{}

\begin{document}

{\ldots{}.34\ldots{}. }

{This is the device. {[} It is known as Shvidhara's method. {]}}

{अलिकुलदमूलं मालतीं यातमष्टौ }

{निखिलनवमभागाश्चालिनी भृङ्गमेकम् । }

{निशि पीरमललुब्धं पद्ममध्ये निरुद्धम् }

{प्रतिरणति रणन्तं ब्रूहि कान्तेऽलिसंख्याम् ।। ११७ ।। }

{From a cluster of black bees square root of half the number and 8/9th
of the cluster went to malati flower. And due to the fragrance one bee
was bound in the lotus at night. And the female bee kept out, is calling
him. Find the number in the cluster.}

{पार्थः कर्णवधाय मार्गणगणं कृद्धो रणे संदधे }

{तस्यार्धेन निवार्य तच्छरगणं मूलैश्चतुर्भिर्हयान् । }

{शल्यं षड्भिरथेषुभिस्त्रिभिरपि च्छत्रं ध्वजं कार्मुकं }

{चिच्छेदास्य शिरः शरेण कति ते यानर्जुनः संदधे ।। ११८ ।। }

{Arjun in anger used some arrows to kill Karna. With half the number he
repelled Karna'a arrows. He killed his horses with arrows equal to four
times the square root. With six he killed Shalya and with three he
destroyed the umbrella, flag and bow. He beheaded Karna with one arrow.
Find how many arrows were used by Arjun.}

{व्येकस्य गच्छस्य दलं किलादिरादेर्दलं तत्प्रचयः फलं च । }

{चयादिगच्छाभिहतिः स्वसप्तभागाधिका ब्रूहि चयादिगच्छान् ।।११९।। }

{Subtracting 1 from the number of terms and dividing by 2 we get the
first term of an A.P. Half the first term is equal to the common
difference. Product of number of the terms, first term and common
difference added to its seventh part gives the sum of the series. Give
the common difference, first term and the number of terms.}

\end{document}
