\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother


\date{}

\begin{document}

{Bhaskaracharya's Bijaganit and its Translation}

{Invocation and Introduction}

{उत्पादकं यतत प्रवदन्ति बुद्धेर् अधिष्ठितं सत् पुरुषेण सांख्याः । }

{ व्यक्तस्य कृत्स्नस्य तदेकबीजम् अव्यक्तमीशं गणितं च वन्दे ।। १ । । }

{I bow with reverence to that unmanifested which the wise (and
mathematicians) regard as the sub-stra-tum of the Being and the source
of intelligence. It is the root cause of this entire world. I bow to the
unmanifested i. e. to God and Mathematics (which has similar
attributes).}

{पूर्वं प्रोक्तं व्यक्तमव्यक्तबीजं }

{प्रायः प्रश्नो नो विनाऽव्यक्तयुक्त्या । }

{ज्ञातुं शक्या मन्दधीभिर्नितान्तं }

{यस्मात् तस्माद् वच्मि बीजक्रियां च ।।२।। }

{Previously has been given arithmetic of which the basis if algebra.
Ordinarily problems cannot be solved without the use of unknowns. As
this is the case with those with limited intelligence, I now give the
process of algebra.}

{ }

{१ धनर्णषड्वधम् । }

{The six rules for positive and negative numbers.}

{योगे युतिः स्यात् क्षययोः स्वयोर् वा धनर्णयोरन्तरमेव योगः ।।३।। }

{Two numbers which may be both positive or both negative can be added by
combining them.}

{रूपत्रयं रूपचतुष्टयं च क्षयं धनं वा सहितं वदाऽऽशु । }

{स्वर्णं क्षयः स्वं च पृथक् पृथङ्मे धनर्णयोः संकलनामवैषि ।।४।।}{\\
}

\end{document}
