\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother


\date{}

\begin{document}

{\ldots{}.39\ldots{}.}

{रूपाणां नवतिर्द्विषष्टिरनयोस्तौ तुल्यवित्तौ तथा }

{बीजज्ञ प्रतिरप्नजानि सुमते मौल्यानि शीघ्रं वद ।। १३५ ।। }

{One man has 5 rubies, 8 saphires, 7 pearls and 90 rupees. Other man has
7 rubies, 9 saphires, 6 pearls and 62 rupees. They were equally rich.
Find the price of each jewel.}

{एको ब्रवीति मम देहि शतं धनेन }

{त्बत्तो भवामि हि सखे द्विगुणस्ततोऽन्यः । }

{ब्रूते दशार्पयसि चेन्मम षड्गुणोऽहं }

{त्वत्तस्तयोवद धने मम किंप्रमाणे ।। १३६ ।।}

{One man says to the other, " Please give me Rs. 100, then my wealth
will be twice your wealth. The other says " If you will give me Rs. 10,
my wealth will be six times your wealth." Find each man's wealth.}

{अश्वाः पञ्चगुणाङ्गमङ्गलमिता येषां चतुर्णां धना }

{त्युष्टाश्च द्विमुनिश्रश्रुतिक्षितिमिता अष्टद्विभूपावकाः । }

{तेषामश्वतरा वृषा मुनिमहीनेत्रेन्दुसंख्याःक्रमात्}

{सर्वे तुल्यधनाश्च ते वद सपद्यश्वादि मौल्यानि मे ।। १३७ ।। }

{There were four persons. One had 5 horses, 2 camels, 8 mules and 7
oxen. Second had 3 horses, 7 camels, 2 mules and 1 ox. Third had 6
horses, 4 camels, 1 mule and 2 oxen. Fourth had 8 horses, 1 camel, 3
mules and 1 ox. All of them became equal in wealth after selling them at
the same rate. Find the price of horse etc.}

{त्रिभिः पारावताः पञ्च पञ्चभिः सप्त सारसाः । }

{सप्तभिर्नव हंसाश्च नवभिर्बर्हिणस्त्रयः । । }

{द्रम्मैरवाप्यते द्रम्मशतेन शतमानय । }

{एषां पारावतादीनां विनोदार्थ महीपतेः ।। १३८ ।। }

{For 3 drammas one can get 5 pigeons, for 5 drammas 7 cranes, for 7
drammas 9 geese and for 9 drammas 3 peacocks. Please buy for the king
100\\
}

\end{document}
