\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother


\date{}

\begin{document}

{ \ldots{}.5\ldots{}.}

{Nimbalkar, Collector, Pune, Mrs. Leena Mehendale, Additional Collector
and Competent Authority and many of our wellwishers who have rendered
all possible help in getting this land. We are confident that
Bhaskaracharya Pratishthana will be able to provide better research
facilities on a permanent basis in near future.}

{During last two years Bhaskaracharya Pratishthana has published two
souvenirs. The second anniversary souvenir published in October 1978
contains a research paper of Professor Shreeram Abhyankar in Hindi. The
foundations of research in Mathematics lie in the rare works of Indian
mathematicians viz. Aryabhatta, Varahamihir Brahmagupta and
Bhaskaracharya. Through this publication Bhaskaracharya Pratishthana is
making available this treasure of knowledge to the readers. Professor S.
K. Abhyankar has translated original work in Sanskrit into English. This
is an humble effort to acquaint the common reader with the origin of
Algebra and we hope that these efforts will be acknowledged.}

{We express over heartfelt gratitude to shri M. S. Alias Baburaoji
Parkhe, our honourable member for making available paper for bringing
out this book.}

{We also thank Shri. Y. G. Joshi and his colleagues of Anand Mudranalaya
for elegant printing of this book. Directors of Shri. Sharada Sahakari
Bank Ltd. and Vidya Sahakari Bank Ltd, have rendered active support to
our work by placing their precious insertions in this book. We thank
them. }

{A. G. jumde}

{Hon. Dy. Director\\
}

\end{document}
