\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother


\date{}

\begin{document}

{Publisher's Foreword}{\\
}

{It gives us a great pleasure in introducing Bhaskaracharya
Pratishthana's maiden publication to lovers of Mathematics all over the
world.}

{Bhaskaracharya Pratishthana has completed four years of its sincere
service to the cause of Mathematics and development of research facility
in Mathematics. For last four years Pratishthana has dedicated itself to
the task of searching talented students in Mathematics and making them
available all possible facilities in undertaking research in
Mathematics. Our founder Director Professor Dr. Shreeram Abhyankar has
been staying in India for last two years and in his presence he has
activated many-folded developmental programme to see his undertaking
through. The ship is sailing slowly but firmly towards the shores of its
goal fighting against unfavourable winds and waves.}

{We are proud to mention that Bhaskaracharya Pratishthana is the only
private body in India which has held two summer programmes on an all
India basis without any aid from external agencies. Students from all
corners of India had participated in these programmes. Professors from
India and abroad came to Poona to deliver lectures and seminars in these
summer programmes. The students and teachers participating in this
activity were provided with lodging and boarding facilities by
Bhaskaracharya Pratishthana.}

{During last two years the library of Bhaskaracharya Pratishthana has
been enriched with the addition of useful and rare books, journals and
research papers.}

{Bhaskaracharya Pratishthana has recently sought the possession of a
piece of land released by Competent Authority, Pune Agglomeration Area.
I take this opportunity to thank Shri. Ajit}

\end{document}
